Based on polling as of 27 October 2024, Harris expects to win on 49%, leads Trump by about 2% in 2024 US election

### 2024-10-31 paper/paper.qmd
update paper on data end date

We conduct our polling data analysis using the R programming language [@citeR]. Our dataset, obtained from FiveThirtyEight [@fivethirtyeight2024], provides a detailed overview of public opinion in the lead-up to the election. Adhering to the guidelines presented in @tellingstories, we explore various factors that influence voter support percentages, including the timing of the polls, the traits of polling organizations, and regional differences.

>>>>

We conduct our polling data analysis using the R programming language [@citeR]. Our dataset, obtained from FiveThirtyEight [@fivethirtyeight2024],based on polling as of 27 October 2024, provides a detailed overview of public opinion in the lead-up to the election. Adhering to the guidelines presented in @tellingstories, we explore various factors that influence voter support percentages, including the timing of the polls, the traits of polling organizations, and regional differences.
